\documentclass[12pt]{article}

\usepackage{times}
\usepackage{graphicx}

\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.9in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\topmargin}{0.05in}
\setlength{\headheight}{-0.05in}
\setlength{\headsep}{0.0in}

\begin{document}

\begin{center}
{\bf CS 6300} \hfill {\large\bf HW05: TD and Q Learning} \hfill {\bf Due March 3, 2022}
\end{center}

\noindent
Please use the \LaTeX\ template to produce your writeups. See the
Homework Assignments page on the class website for details.  Hand in
via gradescope.

Jennifer is currently finishing up in college and is trying to decide
what she wants to do with the rest of her life.  She assumes her
options can be modeled as an MDP, with a discount $\gamma=1/2$.  At
each point in her life she can choose to either continue in school
(action $x$) or try to get a job (action $y$).  Her three states are
{\bf C}ollege, {\bf G}rad School and {\bf J}ob.  {\bf J} is a terminal
state.

Suppose Jennifer doesn't actually know the MDP model.  Instead, she
watched three of her older siblings go through life.  They exhibited
the following episodes.

\begin{center}
\begin{tabular}{|l|l|l|} \hline
{\bf Sibling 1} & {\bf Sibling 2} & {\bf Sibling 3} \\ \hline
    C, x, -200 & C, x, -400 & C, x, -400 \\
    C, x, -200 & G, x,  100 & G, x,  100 \\
    C, y,  400 & G, x,  100 & G, x,  100 \\
    J          & G, y, 1000 & G, x,  200 \\
               & J          & J          \\ \hline
\end{tabular}
\end{center}

  \begin{enumerate}

  \item What are the transition probabilities and rewards that you can
    know about?

  \item Find the values $V(s)$ using direct estimation.

  \item Use TD Learning instead to find estimates of the values,
    assuming $\alpha=1/2^{n-1}$, where $n$ is the sibling number.

  \item Use Q learning instead, and extract the estimated optimal policy.

  \end{enumerate}

\end{document}
